fairmetrics: An R package for group fairness evaluation

### 2025-09-10 utils/joss_paper/paper.Rmd
fixing typo

---
title: 'fairmetrics: An R package for group fairness evaluation'
tags:
  - R
  - Fairness
  - Machine Learning
  - Software
authors:
  - name: Benjamin Smith
    orcid: 0009-0007-2206-0177
    affiliation: 1
  - name: Jianhui Gao
    orcid: 0000-0003-0915-1473
    affiliation: 1
  - name: Benson Chou
    orcid: 0009-0007-0265-033X
    affiliation: 1
  - name: Jessica Gronsbell
    orcid: 0000-0002-5360-5869
    affiliation: 1
affiliations:
  - name: "Department of Statistical Science, University of Toronto"
    index: 1
date: "2025-06-10"
bibliography: paper.bib
output:
  rticles::joss_article:
    keep_tex: true
  md_document:
     #keep_tex: true
     preserve_yaml: TRUE
     variant: "markdown_strict"
journal: JOSS
---

@@

           Fairness Assesment                                  Metric
1          Statistical Parity                Positive Prediction Rate
2           Equal Opportunity                     False Negative Rate
3         Predictive Equality                     False Positive Rate
4  Balance for Positive Class           Avg. Predicted Positive Prob.
5  Balance for Negative Class           Avg. Predicted Negative Prob.
6  Positive Predictive Parity               Positive Predictive Value
7  Negative Predictive Parity               Negative Predictive Value
8          Brier Score Parity                             Brier Score
9     Overall Accuracy Parity                                Accuracy
10         Treatment Equality (False Negative)/(False Positive) Ratio

>>>>

---
title: 'fairmetrics: An R package for group fairness evaluation'
tags:
  - R
  - Fairness
  - Machine Learning
  - Software
authors:
  - name: Benjamin Smith
    orcid: 0009-0007-2206-0177
    affiliation: 1
  - name: Jianhui Gao
    orcid: 0000-0003-0915-1473
    affiliation: 1
  - name: Benson Chou
    orcid: 0009-0007-0265-033X
    affiliation: 1
  - name: Jessica Gronsbell
    orcid: 0000-0002-5360-5869
    affiliation: 1
affiliations:
  - name: "Department of Statistical Sciences, University of Toronto"
    index: 1
date: "2025-06-10"
bibliography: paper.bib
output:
  md_document:
     #keep_tex: true
     preserve_yaml: TRUE
     variant: "markdown_strict"
  rticles::joss_article:
    keep_tex: true
journal: JOSS
---

@@

           Fairness Assessment                                 Metric
1          Statistical Parity                Positive Prediction Rate
2           Equal Opportunity                     False Negative Rate
3         Predictive Equality                     False Positive Rate
4  Balance for Positive Class           Avg. Predicted Positive Prob.
5  Balance for Negative Class           Avg. Predicted Negative Prob.
6  Positive Predictive Parity               Positive Predictive Value
7  Negative Predictive Parity               Negative Predictive Value
8          Brier Score Parity                             Brier Score
9     Overall Accuracy Parity                                Accuracy
10         Treatment Equality (False Negative)/(False Positive) Ratio
